\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-02 paper/sp.tex
intro complete, but terrible

What follows is a regression:
We use \gaia\ measurements of parallax to learn relationships between 
the spectroscopic and photometric properties of stars and their parallaxes.
We then use that learned model to estimate improved parallaxes for stars with
poor (or no) \gaia\ measurements.
This regression is very sensitive to certain aspects of the data or experimental
design..
One is that we will do far better with the regression if we have an accurate
model for noise process in the \gaia\ data.
For this reason, we make use of a justifiable likelihood function for the
\gaia\ astrometry (CITE HOGG).
Another is that we can be strongly biased if we have a bad selection function
or data censoring.
HOGGGGGThis means that we cannot apply cuts to the \gaia\ astrometry or signal-to-noise
unless those cuts are correctly accounted for in our generative model.HOGGG GGG

>>>>

What follows is a regression:
We use \gaia\ measurements of parallax to learn relationships between 
the spectroscopic and photometric properties of stars and their parallaxes.
We then use that learned model to estimate improved parallaxes for stars with
poor (or no) \gaia\ measurements.
This regression is very sensitive to certain aspects of the data or experimental
design..
One is that we will do far better with the regression if we have an accurate
model for noise process in the \gaia\ data.
For this reason, we make use of a justifiable likelihood function for the
\gaia\ astrometry (CITE HOGG).
Another is that regressions can be strongly biased if we have a bad selection function
or data censoring.
This means that we cannot apply cuts to the \gaia\ astrometry or signal-to-noise
unless those cuts are correctly accounted for in our generative model for the
data sample.
Below, we will make no such cuts. That means that our training step has the odd
property that much of the training data is low in signal-to-noise and many of the
training parallax measurements are even negative!
The fact that we are using a justified likelihood function ensures that these
data will only affect the model in sensible and justifiable ways.
The alternative---cutting to high signal-to-noise data---is the more traditional
approach, but it leads to biased inferences (unless the cuts are included correctly
in the likelihood function).
The method in which we make no cuts and keep an umodified, justified likelihood function
is unbiased, and simple.
